Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-30 paper/aldebaran.tex
wording

As a final step to reduce residual uncorrected systematics, we apply the \textsc{k2sc} \citep{k2sc} Gaussian Process-based systematics correction code to the initial halo light curve, but the effect of this in the present case for Aldebaran is minimal.
There is somewhat higher than usual residual noise at multiples of $4 c/d$ (the satellite thruster firing frequency), but this is nevertheless very small in comparison to the signal from Aldebaran, and may be ascribed to the large fraction of the pixel mask occupied by the bleed column from this extremely bright star.

>>>>

As a final step to reduce residual uncorrected systematics, we apply the \textsc{k2sc} \citep{k2sc} Gaussian Process-based systematics correction code to the initial halo light curve, but the effect of this in the present case for Aldebaran is minimal.
There is somewhat higher than usual residual noise at harmonics of $4 c/d$ (the satellite thruster firing frequency), but this is nevertheless very small in comparison to the signal from Aldebaran, and may be ascribed to the large fraction of the pixel mask occupied by the bleed column from this extremely bright star.
